Convolutional Neural Nets for the MNIST Digit Dataset

### 2014-12-13 tex/paper.tex
Add more captions

\begin{figure*}
  \makebox[\textwidth][c]{\includegraphics[scale=0.72]{actfilts}}
  \caption{This is also a tiger.}
  \label{fig:actfilts}
\end{figure*}

>>>>

\begin{figure*}
  \makebox[\textwidth][c]{\includegraphics[scale=0.72]{actfilts}}
  \caption{This presents a snapshot of our two networks when classifying the number three. On the left, the activations and filters for the one convolutional/pooling layer
  architecture is shown, while the activations and filters for two convolutional/pooling layer architecture can be seen on the right. As can be seen by the activation of the 
  first convolutional layer of both networks, the respective filters are essentially acting as edge detectors.}
  \label{fig:actfilts}
\end{figure*}
